\chapter*{Preface}
The idea behind this book is to systematically put a lot of knowledge from different fields in the same place. It is envisioned to serve a purpose of an index book, a glossary introduction to modern physics. The depth may be lacking in some respects but the core idea is to have a background knowledge of many approaches and frameworks.

Physics is a journey. In this book, I've tried to illustrate my own journey
through theoretical physics in hopes that it might help others in their own
studies. 

The book is mainly divided into two parts. The first one is dedicated to
physics. Many topics are considered there - quantum field theory, general
relativity, nonlinear dynamics and a bunch more. Of course, not all topics are
treated equally both in scope and depth. That does not reflect their
importance, it merely reflects the fact that I am more interested in them.
\par The second part is about mathematical preliminaries. Again, some things
are explained in detail and others are only brushed upon. However, I've tried
to include everything that is absolutely \textit{needed} if you would like to
work in theoretical physics.
\par Again, this book is not trying to be exactly pedagogical. It is designed
as an extended handbook, somewhere one can search for a definition, a formula
or a general description of a phenomenon or mathematical idea.
\par It must be noted that this book is, and always will be,
\textbf{completely free}.
You are free to redistribute it, modify it and use it in any way you want,
without asking for permission from the author. The LaTeX file and the
documentation for it are available on
\url{https://github.com/HallowDance/book}. The only thing I'll politely ask
(but not enforce) is that you don't use parts of the book or the book as
a whole for commercial purposes. 


